```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r,include=FALSE}
if (!require("tidyverse")) {
install.packages("tidyverse")
}
if (!require("lubridate")) {
install.packages("lubridate")
}
if (!require("maps")) {
install.packages("maps")
}
if (!require("plotly")) {
install.packages("plotly")
}
if (!require("ggthemes")) {
install.packages("ggthemes")
}
library(ggthemes)
library(plotly)
library(tidyverse)
library(maps)
library(lubridate)
```

```{r}
data<-readxl::read_xlsx('BestInShow.xlsx', sheet='Best in show full sheet')

```

```{r}
data<-data%>%
  select(1,3,5,6,11,32)
data<-data[-(1:3),]
names(data)<-c("breed","category","score","popularity","intelligence","size")
data<-data %>%
  na.omit(data)%>%
  mutate(category=as.factor(category),size=as.factor(size),score= as.numeric(score), popularity = as.numeric(popularity),intelligence = as.numeric(intelligence))%>%
  #42 because dumb is i think lower 50% which a score of 43 was in lower 50% and 41 was higher 50% of trainability 
  mutate(intelligence = ifelse(intelligence<42,"clever","dumb"))
data
```
2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 
```{r}
ggplot(data,aes(x=score,y=-popularity,color=category,size=reorder(size,desc(size)),shape=intelligence))+geom_point(alpha=.8)+labs(y="popularity", title="Best in Show: The Ultimate Data Dog")+ geom_text(aes(label=`breed`),size=2,vjust = -.5, nudge_y = 2)+
  geom_vline(xintercept = 2.33)+geom_hline(yintercept = -75)+ 
  annotate("text",x=1.3,y=10,label="Inexplicably Overrated")+
  annotate("text",x=3.5,y=10,label="Hot Dogs!")+
  annotate("text",x=1.3,y=-160,label="The Rightly Ignored")+
  annotate("text",x=3.3,y=-160,label="Overlooked Treasures")

```

